Component-Based Framework of Lightweight Ruby for Efficient Embedded Software Development

### 2016-10-30 jssst/paper.tex
Editing the text

\begin{figure}[t]
    \centering
    \includegraphics[width=6.5cm,clip]{figure/rotateReadyQueue.eps}
\caption{RiteVM scheduler design}
\label{fig:rotateReadyQueue}
\end{figure}

\begin{figure}[t]
    \centering
    \includegraphics[width=6.5cm,clip]{figure/cyclic_handler.eps}
\caption{Component diagram of RiteVM scheduler}
\label{fig:cyclic_handler}
\end{figure}

@@

@@

\begin{table}[t]
    \centering
\caption{Comparison of size and load process time between an mruby application with and without mruby libraries}
    \scriptsize
    {\tabcolsep=0.1cm
    \begin{tabular}{c||c|c|c}
                        & App\&Lib     & App        &   App\&Lib/App  \\ \hline
        Bytecode Size   & 14,044 bytes & 199 bytes  &   $\times$70.6          \\ %\hline
        Loading Time    & 305.081 msec & 7.774 msec &   $\times$39.2          \\
        Compile Time    & 8.7 msec     & 0.3 msec   &   $\times$29.0          \\
    \end{tabular}
    }
    \label{tab:size_and_time}
\end{table}

@@

A comparison of the application execution time with singletasking, co-routine, and multitasking is shown in Fig.\ref{fig:comparison_s_c_m}.
A program with 100,000 loops was used as an mruby application for the evaluation of execution time.
Here, the singletask program looped 100,000 times and the multitask and co-routine programs looped 50,000 times for each task.

\subsubsection{Execution Time with Singletasking, Co-routine, and Proposed Multitasking}

@@

Fig.\ref{fig:comparison_s_c_m} shows that the proposed design is superior to multitask using delay method and co-routine in terms of execution time.
The {\it delay} and co-routine methods run on a RiteVM, which causes the slowdown compared to the proposed multitasking.
The scheduler runs as the periodic handler of RTOS.
% In Fig.\ref{fig:comparison_s_c_m}, the periodic time of the periodic handler for multitasking is 1 msec.
% This shows that the proposed design is superior to co-routine in terms of execution time.
Moreover, developers can utilize the scheduler practically because the RiteVM scheduler overhead is approximately 5\%.
The scheduler interrupts and switches tasks, which causes this overhead.Although the overhead is larger as the number of RiteVMs increases, it also spreads the difference between multitask and co-routine.
Therefore, the scheduler is the more efficient approach for multitasking than the existing multitasking and co-routine.
Here, the periodic time of the scheduler is 1 msec.
It takes approximately 3 $\mu$sec on average to switch tasks once.

\subsubsection{Periodic Time Overhead}

>>>>

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=6.5cm,clip]{figure/rotateReadyQueue.eps}
\caption{RiteVM scheduler design}
\label{fig:rotateReadyQueue}
\end{figure} 
\begin{figure}[t]
    \centering
    \includegraphics[width=6.5cm,clip]{figure/cyclic_handler.eps}
\caption{Component diagram of RiteVM scheduler}
\label{fig:cyclic_handler}
\end{figure}

@@

\begin{table}[t]
    \centering
\caption{Size and load process time of an mruby application with/without libraries}
    \scriptsize
    {\tabcolsep=0.1cm
    \begin{tabular}{c||c|c|c}
                        & App\&Lib     & App        &   App\&Lib/App  \\ \hline
        Bytecode Size   & 14,044 bytes & 199 bytes  &   $\times$70.6          \\ %\hline
        Loading Time    & 305.081 msec & 7.774 msec &   $\times$39.2          \\
        Compile Time    & 8.7 msec     & 0.3 msec   &   $\times$29.0          \\
    \end{tabular}
    }
    \label{tab:size_and_time}
\end{table}

@@

@@

% A comparison of the application execution time with singletasking, co-routine, and multitasking is shown in Fig.\ref{fig:comparison_s_c_m}.
% A program with 100,000 loops was used as an mruby application for the evaluation of execution time.
% Here, the singletask program looped 100,000 times and the multitask and co-routine programs looped 50,000 times for each task.

%\subsubsection{Execution Time with Singletasking, Co-routine, and Proposed Multitasking}
{%\bf Execution Time with Singletasking, Co-routine, and Proposed Multitasking}

Fig.\ref{fig:comparison_s_c_m} shows that the proposed design is superior to multitask using delay method and co-routine in terms of execution time.
The {\it delay} and co-routine methods run on a RiteVM, which causes the slowdown compared to the proposed multitasking.
The scheduler runs as the periodic handler of RTOS.
% In Fig.\ref{fig:comparison_s_c_m}, the periodic time of the periodic handler for multitasking is 1 msec.
% This shows that the proposed design is superior to co-routine in terms of execution time.

Moreover, developers can utilize the scheduler practically because the RiteVM scheduler overhead is approximately 5\%.
The scheduler interrupts and switches tasks, which causes this overhead.Although the overhead is larger as the number of RiteVMs increases, it also spreads the difference between multitask and co-routine.
Therefore, the scheduler is the more efficient approach for multitasking than the existing multitasking and co-routine.
Here, the periodic time of the scheduler is 1 msec.
It takes approximately 3 $\mu$sec on average to switch tasks once.

%\subsubsection{Periodic Time Overhead}
%{\bf Periodic Time Overhead}
